### 2019-11-06 191016_Paper_Thesis_v2/Experiments.tex
paper_thesis:update

The proposed method's performance, convergence speed, and degradation were compared to those of other traditional methods.
To compare the proposed method's feature extraction performance to that of traditional and deep-learning based methods, feature space was visualized as a 2D Euclidean plane using principal component analysis ("PCA"). 

@@

For handcraft methods' least square estimations ("LSE")~\cite{duda2012pattern}, PCA with LSE~\cite{turk1991eigenfaces}, support vector machine~\cite{vapnik2013nature} and the total error minimization with reduced multivariate polynomials~\cite{toh2003fingerprint,toh2008between} were compared. Parameters were selected that performed optimally in each traditional method. For LSE,SVM, and TER, the input signatures were reduced to 500$\times$30 by averaging the subcarrier axis. For PCA-LSE, the input signature dimension was reduced to 40 following~\cite{moon2017air}. For SVM with a Gaussian kernel function ("RBF"), the kernel's parameters $c$ and $\gamma$ were chosen by a grid search over the range $c\in\{0.01,1,10\}$ and $\gamma\in\{0.01/3000, 0.1/3000, 1/3000, 10/3000, 100/3000\}$. For TER, the parameter M was chosen from among $M\in\{1,2,3\}$ and $\tau=\eta=0.5$ following~\cite{toh2008between}.

@@

Verification performance was evaluated in terms of the equal error rate ("EER"). Random five-runs of two-fold cross-validation tests were conducted.

@@

%roc
The proposed method had the widest area under the receiver operating characteristic ("ROC") curve (Fig.~\ref{fig_roc}).
\begin{figure*}[!ht]
    \includegraphics[width=\textwidth]{fig_roc_v15.eps}
    \caption{Normalized training loss curve.} \label{fig_roc}
\end{figure*}
 %5.3.1. conv speed
\subsection{Convergence Speed}
Fig.~\ref{fig_loss} shows the convergence of the normalized loss function during training. The proposed method had a faster convergence speed than the deep learning based methods, indicating that KAR learning accelerated the learning speed.
 \begin{figure*}[!ht]
    \includegraphics[width=\textwidth]{normalized_loss_curve_ma30_v3.eps}
    \caption{normalized training loss trends} \label{fig_loss}
\end{figure*}
%5.3.2. feature vector
\subsection{Feature Vector Size Effect}
Fig.~\ref{fclayer} shows the EERs for different sizes of feature vectors in the feature space. 
For metric learning systems, feature vector size is generally positively correlated with system performance.
The proposed system's performance was negatively correlated with feature vector size.
\begin{table}[]
    \centering
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    Feature vector size        & 16    & 8     & 4     & 2     \\ \hline
    Siamese network            & 20.34 & 22.05 & 29.39 & 34.26 \\ \hline
    Baseline triplet network   & 18.37 & 19.52 & 19.20 & 24.76 \\ \hline
    Proposed method            & 16.92 & 18.03 & 18.08 & 26.64 \\ \hline
    \end{tabular}
\end{table}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fclayer_v1.eps}
    \caption{Feature Vector Size Effect.} \label{fclayer}
\end{figure}
%5.3.3. 2D visualization of feature vector
\subsection{2D Visualization of the Feature Vectors}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig_2d_triKAR_10_v1.eps}
    \caption{2D Feature Representation : Proposed System.} \label{fig_2d_triKAR_10}
\end{figure}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig_2d_tribase_10_v1.eps}
    \caption{2D Feature Representation : Baseline triplet network.} \label{fig_2d_tribase_10}
\end{figure}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig_2d_siam_10_v1.eps}
    \caption{2D Feature Representation : Siamese network.} \label{fig_2d_siam_10}
\end{figure}
To visualize the proposed system's feature extraction performance, the feature space was projecgted onto two-dimensional Euclidean space using PCA (Figs.~\ref{fig_2d_siam_10},~\ref{fig_2d_triKAR_10}, and~\ref{fig_2d_tribase_10}). each system's feature extraction performance by determining whether proximate points shared the same identity. Only the first 10 identities were visualized to facilitate the visual confirmation process.
The proposed method used the space most efficiently. The Siamese network linearly arranged feature vectors, making it difficult to distinguish between classes. The baseline triplet network caused many identities to overlap.

>>>>

To compare the proposed method's feature extraction performance to that of traditional and deep-learning based methods, feature space was visualized as a 2D Euclidean plane using principal component analysis (``PCA''). 

@@

For handcraft methods' least square estimations (``LSE'')~\cite{duda2012pattern}, PCA with LSE~\cite{turk1991eigenfaces}, support vector machine~\cite{vapnik2013nature} and the total error minimization with reduced multivariate polynomials~\cite{toh2003fingerprint,toh2008between} were compared. Parameters were selected that performed optimally in each traditional method. For LSE,SVM, and TER, the input signatures were reduced to 500$\times$30 by averaging the subcarrier axis. For PCA-LSE, the input signature dimension was reduced to 40 following~\cite{moon2017air}. For SVM with a Gaussian kernel function (``RBF''), the kernel's parameters $c$ and $\gamma$ were chosen by a grid search over the range $c\in\{0.01,1,10\}$ and $\gamma\in\{0.01/3000, 0.1/3000, 1/3000, 10/3000, 100/3000\}$. For TER, the parameter M was chosen from among $M\in\{1,2,3\}$ and $\tau=\eta=0.5$ following~\cite{toh2008between}.

@@

Verification performance was evaluated in terms of the equal error rate (``EER''). Random five-runs of two-fold cross-validation tests were conducted.

@@

%roc
The proposed method had the widest area under the receiver operating characteristic (``ROC'') curve (Fig.~\ref{fig_roc}).
\begin{figure*}[!ht]
    \includegraphics[width=\textwidth]{fig_roc_v15.eps}
    \caption{Normalized training loss curve.} \label{fig_roc}
\end{figure*}
 %5.3.1. conv speed
\subsection{Convergence Speed}
Fig.~\ref{fig_loss} shows the convergence of the normalized loss function during training. The proposed method had a faster convergence speed than the deep learning based methods, indicating that KAR learning accelerated the learning speed.
 \begin{figure*}[!ht]
    \includegraphics[width=\textwidth]{normalized_loss_curve_ma30_v3.eps}
    \caption{normalized training loss trends} \label{fig_loss}
\end{figure*}
%5.3.2. feature vector
\subsection{Feature Vector Size Effect}
Fig.~\ref{fclayer} shows the EERs for different sizes of feature vectors in the feature space. 
For metric learning systems, feature vector size is generally positively correlated with system performance.
The proposed system's performance was negatively correlated with feature vector size.
\begin{table}[]
    \centering
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    Feature vector size        & 16    & 8     & 4     & 2     \\ \hline
    Siamese network            & 20.34 & 22.05 & 29.39 & 34.26 \\ \hline
    Baseline triplet network   & 18.37 & 19.52 & 19.20 & 24.76 \\ \hline
    Proposed method            & 16.92 & 18.03 & 18.08 & 26.64 \\ \hline
    \end{tabular}
\end{table}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fclayer_v1.eps}
    \caption{Feature Vector Size Effect.} \label{fclayer}
\end{figure}
%5.3.3. 2D visualization of feature vector
\subsection{2D Visualization of the Feature Vectors}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig_2d_triKAR_10_v1.eps}
    \caption{2D Feature Representation : Proposed System.} \label{fig_2d_triKAR_10}
\end{figure}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig_2d_tribase_10_v1.eps}
    \caption{2D Feature Representation : Baseline triplet network.} \label{fig_2d_tribase_10}
\end{figure}
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig_2d_siam_10_v1.eps}
    \caption{2D Feature Representation : Siamese network.} \label{fig_2d_siam_10}
\end{figure}
To visualize the proposed system's feature extraction performance, the feature space was projecgted onto two-dimensional Euclidean space using PCA (Figs.~\ref{fig_2d_siam_10},~\ref{fig_2d_triKAR_10}, and~\ref{fig_2d_tribase_10}). each system's feature extraction performance by determining whether proximate points shared the same identity. Only the first 10 identities were visualized to facilitate the visual confirmation process.
The proposed method used the space most efficiently. The Siamese network linearly arranged feature vectors, making it difficult to distinguish between classes. The baseline triplet network caused many identities to overlap.

### 2019-11-06 191016_Paper_Thesis_v2/Introduction.tex
paper_thesis:update

\section{Background}
% signature
Written signatures have long been used as an identification tool and various methods for verifying individuals base on them have been developed~\cite{fahmy2010online,galbally2015line,sanmorino2012survey,sesa2012information}.
% biometric
The use of biometric identity verification is growing with the popularity of mobile devices. Biometric identity verification systems are more secure, convinient, and provide greater accountability than traditional complex passwords~\cite{hutton2004biometrics}.
% camera sensor
In-air signatures have become possible with the development of specialized sensors, such as depth cameras and magnetic sensors~\cite{bailador2011analysis, jeon2012system,ketabdar2012magnetic,malik20183dairsig}.
% WiFI CSI
In-air signatures can be made using Wi-fi Channel State Information ("CSI") signals. Typically people make a certain gesture when signing their signature on a piece of paper. With in-air signatures, people simply make the same gesture in the air. Their movements are detected by Wi-fi receivers with appropriate software installed. The software detects changes in the Wi-fi signals caused by hand movements. This technique uses widespread devices, so it does not require the use of any special input devices. 
\cite{abdelnasser2015wigest,nandakumar2014wi} used CSI signals to recognize users' gestures and~\cite{moon2017air} used them to specifically identify signatures written in the air. 
However, due to limitations of the traditional feature extractor,~\cite{moon2017air} was only able to identify in-air signatures entering from the specific direction. This makes the user difficult to input their signatures.
% Deep learning
Recent studies have been conducted on the feasibility of using deep learning technology to characterize CSI signals. Deep learning-based models are popular often studied as solutions to this situaiton because of their automated feature extractors and the fact that they have superior classification capabilities than traditional models. Deep learning has been used to recognize users based on their body shape~\cite{pokkunuru2018neuralwave} and behavior~\cite{shi2017smart}.
% our methods
In this thesis, deep learning technology was used to create a Wi-Fi CSI system that can recognize a user's identity with multi-direction in-air signatures.
The deep learning model tested in this study used a triplet network to increase classification and feature extraction accuracy, and to improve the model's convergence speed using the kernel and range space learning techniques~\cite{toh2018gradient}.

%\newpage
\newpage
\section{Motivation and Contributions}
The main contributions of this thesis were
\begin{itemize}
\item Proposing a system to verify user identities using Wi-Fi handwritten signature signals using a deep triplet network;
\item Using the kernel and range (KAR) space learning to mine distinctive triplet inputs which boost convergence speed and reduce triplet network training loss; and
\item Empirically testing the proposed system on a dataset of Wi-Fi handwritten signatures collected from 98 subjects.
\end{itemize}

\section{Paper Organization}
The rest of this paper is organized as follows.  Section 2 discusses related works about triplet networks and KAR space learning. Section 3 discusses the proposed system. Section 4 describes this thesis's experimental and analysis results. Section 5 concludes the thesis.

>>>>

\section{Background}
% signature
Handwritten signatures have long been used as an identification tool and various methods for verifying individuals based on them have been developed~\cite{fahmy2010online,galbally2015line,sanmorino2012survey,sesa2012information}.
% biometric
The use of biometric identity verification is growing with the popularity of mobile devices. Biometric identity verification systems are more secure, convinient, and provide greater accountability than traditional passwords~\cite{hutton2004biometrics,jain2006biometrics,ross2006handbook}.
% camera sensor
In-air signatures have become possible with the development of specialized sensors, such as depth cameras and magnetic sensors~\cite{bailador2011analysis, jeon2012system,ketabdar2012magnetic,malik20183dairsig}.
% WiFI CSI
Recently, the in-air signatures can also be acquired using the Wi-fi Channel State Information (``CSI'') signals. Typically the user makes a certain gesture when signing their signature on a piece of paper. With in-air signatures, the user simply makes the same gesture in the air. Their movements are detected by Wi-fi receivers with appropriate software installed. The software detects changes in the Wi-fi signals caused by the hand movements. This technique uses the existing widespread Wi-Fi devices, so it does not require the use of any special input devices. 
\cite{abdelnasser2015wigest,nandakumar2014wi} used CSI signals to recognize users' gestures and~\cite{moon2017air} used them to specifically identify signatures written in the air. 
However, due to limitations of the traditional feature extractor,~\cite{moon2017air} was only able to identify in-air signatures entering from a specific direction. This makes the user difficult to input their signatures.
% Deep learning
Recent studies have been conducted on the feasibility of using deep learning to characterize the CSI signals. Deep learning-based models are popular because of their automated feature extractors and the fact that they have superior classification capabilities than traditional models. Deep learning has been used to recognize users based on their vital sign~\cite{zhang2017pulseprint,szankin2018long} and behavior~\cite{shi2017smart,pokkunuru2018neuralwave}.
% our methods
In this thesis, the deep learning technology is used to create a Wi-Fi CSI system that can recognize a user's identity with multi-direction in-air signatures.
The deep learning model tested in this study is a triplet network where our task is to improve the model's convergence speed using the kernel and range space learning technique~\cite{toh2018gradient}.

%\newpage
\newpage
\section{Motivation and Contributions}
The main contributions of this thesis
\begin{itemize}
\item Proposing a system to verify user identities using Wi-Fi handwritten signature signals using a deep triplet network;
\item Using the kernel and range (KAR) space learning to mine distinctive triplet inputs which boost convergence speed and reduce triplet network training loss; and
\item Empirically testing the proposed system on a dataset of Wi-Fi handwritten signatures collected from 98 subjects.
\end{itemize}

\section{Paper Organization}
The rest of this thesis is organized as follows.  Section 2 discusses related works about triplet networks and KAR space learning. Section 3 discusses the proposed system. Section 4 describes this thesis's experimental and analysis results. Section 5 concludes the thesis.

### 2019-11-06 191016_Paper_Thesis_v2/Proposed_Method.tex
paper_thesis:update

\label{chp:Method}
% 4.2. Data Acquisition
\section{Preprocessing}
\label{sec:preprocessing}
Wi-Fi signature data must be pre-processed to be used as an input in the proposed system.
First, data must be simplified. In this study, only the magnitude of the complex signal was utilized due to device firmware issues with the phase value of the 2.4Ghz Wi-Fi signal~\cite{wang2015understanding}.
Second, the data must be made to be the same size. All signals have different lengths, so equal length sampling was used to ensure that all data had the same length.
Third, outliers must be addressed. Wi-Fi signals are interrupted by other electromagnetic radiation of which burst noise~\cite{wang2015understanding} can have significant effects. Thus, only data within one standard deviation of the median were analyzed to minimize the effects of burst noise.
% 4.3. Proposed Methodology
\section{Proposed Methodology}
\label{sec:methodology}
%purpose
This thesis proposed an identity verification system based on the Wi-Fi signals produced by in-air handwritten signatures ("Wi-Fi signature"). 
%function
Triplet networks which utilized ConvNet as the feature extractor were used to learn the direction-invariant deep representations of in-air signatures~\cite{hoffer2015deep}. KAR space learning was used to mine triplet inputs to achieve faster loss convergence~\cite{toh2018learning,toh2018gradient}. 
% figure
\begin{figure*}[!ht]
    \includegraphics[width=\textwidth]
        {fig_system_overview_v1.pdf}
    \caption{An overview of the proposed methodology.} \label{fig1}
\end{figure*}
Figure~\ref{fig1} shows an overview of the proposed system. 
KAR space projection learning is used to mine hard samples from the training dataset to create triplets (Fig.~\ref{fig1}(a)). The anchor sample is randomly selected from the training dataset. The hard samples are those which are likely to be misclassified by the triplet network for a given anchor sample.
After the data is selected, the triplet network (Fig.~\ref{fig1}(b)) is trained based on the network output vector distance comparison (Fig.~\ref{fig1}(c)).
% following~
The following subsections discuss the triplet network architecture, triplet loss, and triplet mining using KAR space learning.

@@

% 4.4.2. Triplet mining
\subsection{Triplet Mining Based on KAR Space Learning}
% purpose
To train the triplet network faster, a sub-network for mining the hard positive and negative samples from the training dataset was trained.
% hard sample
The hard positive sample is likely to be misclassified as a negative sample by the triplet network (Fig.~ref{fig2}).
The distance between the feature vectors of the anchor and hard positive samples is larger than other positive samples.
The hard negative sample is likely to be misclassified as a positive sample because the distance between the feature vectors of the anchor and the hard negative sample is smaller than the difference between the feature vectors of the anchor and other negative samples.
Hard triplet inputs are made by combining hard positive and hard negative samples with selected anchor samples. Using hard triplets as triplet network inputs more easily, satisfies~\ref{triplet_condition}. However, before training the triplet network, it is impossible to identify hard samples.
% figure
\begin{figure*}[!ht]
    \includegraphics[width=\textwidth]
        {fig_hardsample_v1.pdf}
    \caption{Selection of hard samples.} \label{fig2}
\end{figure*}
% functions
In order to make hard triplets before tranining the triplet network, a smaller sub-network was trained before training the main triplet network.
This smaller sub-network was made of an MLP and was trained using KAR space learning. As KAR space learning has no backpropagation and no iterative learning process, it was trained all at once on the entire training dataset $X$. 
The sub-network output was defined as: 
\begin{equation}
    KAR\left(\mathbf{X}\right)=\sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\cdot\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(n-1)}\right)\right]\mathbf{W}_{n}\right).
\end{equation}
After training the sub-network, the hard samples were mined by measuring the $L2$ distance between every output vector of the sub-network and the output vector of anchor sample.
The sub-network output for a given anchor sample $x_0$ was $KAR(x_0)$. To mine hard-positive samples, one sample was selected from among the sub-network outputs for which the distance to the anchor feature vector $KAR(x_0)$ was larger than $t_+$. Hard-negative samples were chosen, from among the sub-network outputs for which the anchor feature vector was smaller than $t_-$.
The selected hard-positive and hard-negative samples satisfied the following properties, respectively:
\begin{equation}
    {\left\| {{KAR\left(\mathbf{x}_{0}\right)} - {KAR\left(\mathbf{x}_{+}\right)}} \right\|_2^2} \geq \mathrm{t}_{+}, 
    \label{thres_pos}
\end{equation}
\begin{equation}
    {\left\| {{KAR\left(\mathbf{x}_{0}\right)} - {KAR\left(\mathbf{x}_{-}\right)}} \right\|_2^2} \leq \mathrm{t}_{-},\label{thres_neg}
\end{equation}
If the hardest sample, outlier data is more likely to be selected than other data, resulting in an increased risk of overfitting~\cite{schroff2015facenet}.
To avoid this problem, the threshold for the hard-positive and the hard-negative samples were empirically chosen as the 25th and 75th percentiles of the distance between the anchor and sub-network outputs.

>>>>

\label{chp:Method}
% 4.2. Data Acquisition
\section{Preprocessing}
\label{sec:preprocessing}
Wi-Fi signature data must be pre-processed to be used as an input in the proposed system.
In this study, only the magnitude of the complex signal was utilized due to device firmware issues with the phase value of the 2.4Ghz Wi-Fi signal~\cite{wang2015understanding}.
Second, the data must be made to be the same size. All signals have different lengths, so equal length sampling was used to ensure that all data had the same length.
Third, outliers must be addressed. Wi-Fi signals are interrupted by other electromagnetic radiation of which burst noise~\cite{wang2015understanding} can have significant effects. Thus, only data within one standard deviation of the median were analyzed to minimize the effects of burst noise.
% 4.3. Proposed Methodology
\section{Proposed Methodology}
\label{sec:methodology}
%purpose
This thesis proposed an identity verification system based on the Wi-Fi signals produced by in-air handwritten signatures (``Wi-Fi signature''). 
%function
Triplet networks which utilized ConvNet as the feature extractor were used to learn the direction-invariant deep representations of in-air signatures~\cite{hoffer2015deep}. KAR space learning was used to mine triplet inputs to achieve faster loss convergence~\cite{toh2018learning,toh2018gradient}. 
% figure
\begin{figure*}[!ht]
    \includegraphics[width=\textwidth]
        {fig_system_overview_v1.pdf}
    \caption{An overview of the proposed methodology.} \label{fig1}
\end{figure*}
Figure~\ref{fig1} shows an overview of the proposed system. 
KAR space projection learning is used to mine hard samples from the training dataset to create triplets (Fig.~\ref{fig1}(a)). The anchor sample is randomly selected from the training dataset. The hard samples are those which are likely to be misclassified by the triplet network for a given anchor sample.
After the data is selected, the triplet network (Fig.~\ref{fig1}(b)) is trained based on the network output vector distance comparison (Fig.~\ref{fig1}(c)).
% following~
The following subsections discuss the triplet network architecture, triplet loss, and triplet mining using KAR space learning.

@@

% 4.4.2. Triplet mining
\subsection{Triplet Mining Based on KAR Space Learning}
% purpose
To train the triplet network faster, a sub-network for mining the hard positive and negative samples from the training dataset was trained.
% hard sample
The hard positive sample is likely to be misclassified as a negative sample by the triplet network (Fig.~\ref{fig2}).
The distance between the feature vectors of the anchor and hard positive samples is larger than other positive samples.
The hard negative sample is likely to be misclassified as a positive sample because the distance between the feature vectors of the anchor and the hard negative sample is smaller than the difference between the feature vectors of the anchor and other negative samples.
Hard triplet inputs are made by combining hard positive and hard negative samples with selected anchor samples. Using hard triplets as triplet network inputs more easily, satisfies~\ref{triplet_condition}. However, before training the triplet network, it is impossible to identify hard samples.
% figure
\begin{figure*}[!ht]
    \includegraphics[width=\textwidth]
        {fig_hardsample_v2.pdf}
    \caption{Selection of hard samples.} \label{fig2}
\end{figure*}
% functions
In order to make hard triplets before tranining the triplet network, a smaller sub-network was trained before training the main triplet network.
This smaller sub-network was made of an MLP and was trained using KAR space learning. As KAR space learning has no backpropagation and no iterative learning process, it was trained all at once on the entire training dataset $X$. 
The sub-network output was defined as: 
\begin{equation}
    KAR\left(\mathbf{X}\right)=\sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\cdot\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(n-1)}\right)\right]\mathbf{W}_{n}\right).
\end{equation}
After training the sub-network, the hard samples were mined by measuring the $L2$ distance between every output vector of the sub-network and the output vector of anchor sample.
The sub-network output for a given anchor sample $x_0$ was $KAR(x_0)$. To mine hard-positive samples, one sample was selected from among the sub-network outputs for which the distance to the anchor feature vector $KAR(x_0)$ was larger than $t_+$. Hard-negative samples were chosen, from among the sub-network outputs for which the anchor feature vector was smaller than $t_-$.
The selected hard-positive and hard-negative samples satisfied the following properties, respectively:
\begin{equation}
    {\left\| {{KAR\left(\mathbf{x}_{0}\right)} - {KAR\left(\mathbf{x}_{+}\right)}} \right\|_2^2} \geq \mathrm{t}_{+}, 
    \label{thres_pos}
\end{equation}
\begin{equation}
    {\left\| {{KAR\left(\mathbf{x}_{0}\right)} - {KAR\left(\mathbf{x}_{-}\right)}} \right\|_2^2} \leq \mathrm{t}_{-},\label{thres_neg}
\end{equation}
If the hardest sample, outlier data is more likely to be selected than other data, resulting in an increased risk of overfitting~\cite{schroff2015facenet}.
To avoid this problem, the threshold for the hard-positive and the hard-negative samples were empirically chosen as the 25th and 75th percentiles of the distance between the anchor and sub-network outputs.

### 2019-11-06 191016_Paper_Thesis_v2/Related_Works.tex
paper_thesis:update

\label{chp:Preliminary}
%3.1 Deep Metric Learning
\section{Deep Metric Learning}
% What is metric running?
Metric learning converts multi-dimensional data to group data in a feature space.
% Recent Trends
It has been used for computer vision tasks such as image classification and content-based image retrieval~\cite{yang2006distance}. In the past, features were extracted and similarity was measured using traditional algorithms like HOG and LBP. Rescently, deep learning-based methods have been widely used instead as they have enabled feature extraction and metric learning in a single framework~\cite{yi2014deep}. The deep networks automatically learns image classification features.
% Target Model
Deep learning-based models include the Siamise network and the Triplet network.

%3.1.1 Triplet network
\subsection{Triplet Network}
% Triplet Network
Triplet network is a metric learning model which group triplet data in a feature space~\cite{weinberger2006distance,yang2006distance}.
It is widely used to identify a person based on  several images in a process known as person re-identification, which is similar to butis more challanging than biometric identification due to the low quality and high variety of input images~\cite{yi2014deep}. Other factors, such as changing clothes, poses, and image angles makes it difficult to identify the target person in question.

% training triplet network
Triplet data is composed of anchor, positive, and negative data points. Training of the triplet network involves the creation of feature vectors to be placed in the appropriate feature space in which positive data is close to the anchor and negative data is far from the anchor.
% optimize training
It may not be necessary to train an algorithm using a large number of triplets. Training can be optimized by using only the most learning-efficient triplet. \cite{cheng2016person,ding2015deep,wang2016joint} used triplet networks with used triplets for only a small number of classes, which were used in a random order.
Recently,~\cite{schroff2015facenet} used triplet mining to speed up convergence. They selected inputs from a large set at each training iteration using the network.
However, these sets required the availability of a large amount of training data. This type of training requires the use of large amounts of data separated into only a few classes. Empirical data is not suitable for this type of training strategy because there is usually not enough of it and it is divided into too many classes.
The kernel and range space manipulation methods were used for training to reduce the number of required triplets.

@@

%3.2. KAR
\section{the Kernel and the Range space learning}
% MLP and gradient
Multi Layer Perceptron (MLP) neural networks have been widely used in machine learning. In general, MLPs are trained using the gradient descent and backpropagation methods~\cite{goodfellow2016deep}.
Learning parameters, such as learning rate and momentum value, have a significant impact on gradient descent performance, they must be set carefully.
However, finding the best values through trial and error is time-consuming.

% KAR
Recently, gradient-free learning frameworks for MLP have been developed which rely on KAR space manipulation~\cite{toh2018analytic,toh100,toh2018learning,toh2018gradient}.
This learning framework is based on linear algebra and pseudo-inverse functions, so it does not require any parameters or iterations.

% KAR learning method
Given $m$ samples, the training dataset can be denoted by $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ and the network output can be denoted by $\tilde{Y}$. An MLP network composed of $n-1$ hidden layers $\{ h_{1},\dotsc,h_{n-1} \}$ can be represented by the following equation:
\begin{equation}
    \tilde{Y}=\sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(n-1)}\right)\right]\mathbf{W}_{n}\right)
\end{equation}
where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{n}\in{\mathbb{R}}^{(h_{(n-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.
This network can be trained by adopting the one-hot encoded target matrix $\tilde{Y}\in{\mathbb{R}}^{m \times n}$ instead of network output $\tilde{Y}$. The weighted matrices $\mathbf{W}_{i}$ trained using KAR space manipulation learning can be written as follows~\cite{toh2018gradient}:
\begin{IEEEeqnarray}{rCl}
    \mathbf{W}_{i}&=&\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right), \nonumber \\ i&=&1,\dotsc,n.
\end{IEEEeqnarray}

>>>>

\label{chp:Preliminary}
%3.1 Deep Metric Learning
\section{Deep Metric Learning}
% What is metric running?
Metric learning converts multi-dimensional data to group data in a feature space.
% Recent Trends
It has been used for computer vision tasks such as image classification and content-based image retrieval~\cite{yang2006distance}. In the past, features were extracted and similarity was measured using traditional algorithms like HOG and LBP. Rescently, deep learning-based methods have been widely used instead as they have enabled feature extraction and metric learning in a single framework~\cite{yi2014deep}. The deep networks automatically learns image classification features.
% Target Model
Our focus in this thesis is the Triplet network.

%3.1.1 Triplet network
\subsection{Triplet Network}
% Triplet Network
Triplet network is a metric learning model which group triplet data in the feature space~\cite{weinberger2006distance,yang2006distance}.
It is widely used to identify a person based on  several images in a process known as person re-identification, which is more challanging than biometric identification due to the low quality and high variety of input images~\cite{yi2014deep}. Other factors, such as variation of clothes, poses, and image angles makes it difficult to identify the target person in question.

% training triplet network
The triplet data is composed of anchor, positive, and negative data points. Training of the triplet network involves the creation of feature vectors to be placed in the appropriate feature space in which positive data is close to the anchor and negative data is far from the anchor.
% optimize training
It may not be necessary to train an algorithm using a large number of triplets. Training can be optimized by using only the most learning-efficient triplet. \cite{cheng2016person,ding2015deep,wang2016joint} used triplet networks with used triplets for only a small number of classes, which were used in a random order.
Recently,~\cite{schroff2015facenet} used triplet mining to speed up convergence. They selected inputs from a large set at each training iteration using the network.
However, these sets required the availability of a large amount of training data. This type of training requires the use of large amounts of data separated into only a few classes. Empirical data is not suitable for this type of training strategy because there is usually not enough of it and it is divided into too many classes.
The kernel and range space manipulation methods were used for training to reduce the number of required triplets.

@@

%3.2. KAR
\section{the Kernel and the Range space learning}
% MLP and gradient
Multi Layer Perceptron (``MLP'') neural networks have been widely used in machine learning. In general, the MLPs are trained using the gradient descent and backpropagation~\cite{goodfellow2016deep}.
Learning parameters, such as learning rate and momentum value, have a significant impact on gradient descent performance, they must be set carefully.
However, finding the best values through trial and error is time-consuming.

% KAR
Recently, a gradient-free learning framework for MLP have been developed which rely on KAR space manipulation~\cite{toh2018analytic,toh100,toh2018learning,toh2018gradient}.
This learning framework is based on linear algebra and pseudo-inverse functions, so it does not require any iterations.

% KAR learning method
Given $m$ samples, the training dataset can be denoted by $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ and the network output can be denoted by $\tilde{Y}$. An MLP network composed of $n-1$ hidden layers $\{ h_{1},\dotsc,h_{n-1} \}$ can be represented by the following equation:
\begin{equation}
    \tilde{Y}=\sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(n-1)}\right)\right]\mathbf{W}_{n}\right)
\end{equation}
where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{n}\in{\mathbb{R}}^{(h_{(n-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.
This network can be trained by adopting the one-hot encoded target matrix ${Y}\in{\mathbb{R}}^{m \times n}$. The weighted matrices $\mathbf{W}_{i}$ trained using KAR space manipulation learning can be written as follows~\cite{toh2018gradient}:
\begin{IEEEeqnarray}{rCl}
    \mathbf{W}_{i}&=&\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right), \nonumber \\ i&=&1,\dotsc,n.
\end{IEEEeqnarray}

### 2019-11-06 191016_Paper_Thesis_v2/abstract.tex
paper_thesis:update

\begin{center}
	\LARGE An In-Air Signature Identification System using Commercial Wi-Fi Devices
\end{center}

@@

Identity verification using Wi-Fi in-air handwritten signature is a challenging task in signature verification since the shape of the signal varies according to the direction in which the signature is written.
By using the traditional methods, it was difficult to verify identity from signatures entered in various directions. Moreover, limited size of the dataset also limited the training of deep learning models.
In this paper, we propose a method for identity verification from Wi-Fi in-air signatures based on triplet network. Three-channel ConvNet structures is adopted to learn discriminative features from relatively small size of in-air signature datasets. Moreover, we propose a input triplet mining approach based on the kernel and range space learning to faster the convergence speed.
Our experimental results on the Wi-Fi CSI signature dataset shows that the proposed method out-outperforms both the traditional and deep learning based methods by improved verification accuracy and faster loss convergence.

\vspace{\stretch{1}}
\noindent
\hrulefill\\
{\bf Key words : In-air handwritten signature verification, Wi-Fi Channel State Information, triplet network and the Kernel and Range space learning}
\parbox[t]{0.8\textwidth}
{}

>>>>

\begin{center}
	\LARGE Improving the Triplet Network for Wi-Fi Based Handwritten Signature Verification
\end{center}

@@

Identity verification using Wi-Fi signals is a challenging task since the shape of the signal varies according both the orientation and the position of the user. In this thesis, a system for identity verification is developed based on the hand gesture signature signals sensed by the Wi-Fi Channel State Information (``CSI'').
A three-channel ConvNet structure is adopted to learn the discriminative features based on a relatively small size in-air handwritten signature dataset. We propose an input triplet mining based on the kernel and range space learning to improve the convergence speed of the triplet network training.
Our experimental results on the Wi-Fi CSI signature dataset shows encouraging accuracy and convergence performances.

\vspace{\stretch{1}}
\noindent
\hrulefill\\
{\bf Key words : In-air handwritten signature verification, Wi-Fi Channel State Information, Triplet network, and the Kernel and Range space learning}
\parbox[t]{0.8\textwidth}
{}
